Wolbachia, Toxoplasma and O. Cordyceps: Extreme Host-Manipulating Microbes That Changed the World

### 2015-12-16 paper.tex

- Cordyceps has been studied to make an immuno-surpressant drug

>>>>

- Cordyceps has been studied to make an immuno-surpressant drug
A cousin of the ant manipulating fungus, \textit{Cordyceps sinensis} has been a cornerstone of Chinese medicine for centuries. It has been claimed it can be used to treat many things including respiration and pulmonary diseases, renal, liver, and cardiovascular diseases, hypo sexuality, and hyperlipidemia. Most of these purported benefits have yet to be sufficiently investigated since interest from the western world only began to increase in the last two decades. \cite{medicinal_cordy} Another Cordyceps species, \textit{Cordyceps subsessilus} was used to create the immunosuppresive drug cyclosporin, which is widely used in organ transplantation. The drug prevents the rejection of the foreign organ by interfering with the growth of T cells and the activity of the immune system.\cite{cordy_tcells}
